Saturday mornings with Tufte

### 2022-02-08 _posts/2022-02-05-saturday-mornings-with-tufte/saturday-mornings-with-tufte.Rmd
text tweak

One of the things I love about data science is that this principle is equally critical in both the quantitative and qualitative aspects of our field. Statistical and engineering skills help strip away unneeded or irrelevant data; information design skills help visually present only what is the most important of what remains.

>>>>

One of the things I love about data science is that this principle is equally critical in both the quantitative and qualitative aspects of the field. Statistical and engineering skills help strip away unneeded or irrelevant data; information design skills help visually present only what is the most important of what remains, to deliver the message as clearly as possible.
